\chapter{Ethical Analysis}
\begin{itemize}
\item Ethical
\begin{itemize}
\item There are no real ethical questions because there is no outcome that could have an immoral aspect.
\end{itemize}
\item Social
\begin{itemize}
\item This could have an impact on society because it could decrease the amount of time people spend at malls or other places due to more efficient navigation of a building. People might spend less time in public, will less likely run into people at the mall or other places, and overall reduce person-to-person contact. It could also reduce the amount of impromptu purchases from businesses because people will not have to walk by unnecessary stores.
\end{itemize}
\item Political
\begin{itemize}
\item There are no real political questions because this will not affect government at any level besides maybe easier navigation in their buildings.
\end{itemize}
\item Economic
\begin{itemize}
\item The cost of development will be relatively low because iBeacons are inexpensive, easy to maintain, and the framework can be reproduced as many times as you want for no extra cost.
\end{itemize}
\item Health and Safety
\begin{itemize}
\item There are no real risks to Health and Safety questions because bluetooth is safe for public use.
\item A potential benefit is that it could allows Emergency Medical Services to quickly navigate buildings to have a better response to a critical situation.
\end{itemize}
\item Manufacturability
\begin{itemize}
\item iBeacons are an existing product and the framework requires no manufacturing.
\end{itemize}
\item Sustainability
\begin{itemize}
\item iBeacons' batteries can be sustained for several years on average so they won't need to be replaced very often.
\end{itemize}
\item Environmental Impact
\begin{itemize}
\item There will be minimal waste but once an iBeacon dies it will need to be recycled.
\end{itemize}
\item Usability
\begin{itemize}
\item Our framework will be easy to use for developers to help them design excellent applications.
\end{itemize}
\item Lifelong learning
\begin{itemize}
\item This project will help our group to continually learn how to gain knowledge outside a traditional lecture.
\end{itemize}
\item Compassion
\begin{itemize}
\item This project has a compassionate side because it will help reduce the stress for developers creating location based apps and reduce stress for users when navigating inside buildings.
\end{itemize}
\end{itemize}
